Retrofitting Effect Handlers onto OCaml

### 2021-03-14 retro-concurrency.tex
make the example standalone (Queue.empty -> Queue.Empty as well)

\begin{lstlisting}[numbers=left]
let run main =
  let runq = Queue.create () in
  let suspend k =
    Queue.push (fun () -> continue k ()) runq
  in
  let pending_reads = ref [] in
  let rec run_next () =
    match Queue.pop runq with
    | f -> f ()
    | exception Queue.empty ->
      begin match !pending_reads with
      | [] -> () (* no pending reads *)
      | todo ->
        let compl,todo = do_reads todo in
        List.iter (fun (str,k) ->
          Queue.push (fun () -> continue k str) runq) compl;
        pending_reads := todo;
        run_next ()
      end
  in
  let rec spawn f =
    match f () with
    ...
    | effect (Read ic) k ->
        pending_reads := (ic,k) :: !pending_reads;
        run_next ()
  in
  ...
\end{lstlisting}

>>>>

\begin{lstlisting}[numbers=left]
let run main =
  let runq = Queue.create () in
  let suspend k =
    Queue.push (fun () -> continue k ()) runq
  in
  let pending_reads = ref [] in
  let rec run_next () =
    match Queue.pop runq with
    | f -> f ()
    | exception Queue.Empty ->
      match !pending_reads with
      | [] -> () (* no pending reads *)
      | todo ->
        let compl,todo = do_reads todo in
        List.iter (fun (str,k) ->
          Queue.push (fun () -> continue k str) runq) compl;
        pending_reads := todo;
        run_next ()
  in
  let rec spawn f =
    match f () with
    | () -> run_next () (* value case *)
    | effect Yield k -> suspend k; run_next ()
    | effect (Fork f') k -> suspend k; spawn f'
    | effect (Read ic) k ->
        pending_reads := (ic,k) :: !pending_reads;
        run_next ()
  in
  spawn main
\end{lstlisting}
